Nonparametric Noise models for the Gaussian Process

### 2012-08-09 notes/paper.tex
Updates to the notes.

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Nonparametric Noise models for the Gaussian Process}

@@

We can perform inference in this model using a collapsed Gibbs sampler. In order to work with the CRP representation of the Dirichlet process we introduce a new variable $z_t$ which will represent CRP partition that datapoint $t$ belongs to.

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Nonparametric Noise Models for the Gaussian Process}

@@

We can perform inference in this model using a collapsed Gibbs sampler. In order to work with the CRP representation of the Dirichlet process we introduce a new variable $z_t$ which will represent CRP partition that datapoint $t$ belongs to. For each CRP partition $n$ we represent the cluster parameters using $\theta_n$.

\begin{algorithm}[tb]
   \caption{Collapsed Gibbs Sampling}
   \label{alg:cgibbs}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $\bm{x}, \bm{y}$ and kernel $\bm{K}(\bm{x},\bm{x})$
   \STATE {\bfseries Initialisation:} $z_t \sim \textrm{CRP}(\alpha)$, $\theta_n \sim H$
   \REPEAT
   \STATE Sample $z_t | \bm{K}, \bm{y}, \bm{z}_{\lnot t}, \bm{\theta}$
   \STATE Sample $\theta_n | \bm{x}, \bm{y}, \bm{\theta}$
   \UNTIL convergence
\end{algorithmic}
\end{algorithm}

In algorithm~\ref{alg:cgibbs} we integrate out the Gaussian process $\bm{f}$. In what follows we derive the resampling steps for $z_t$ and $\theta_n$.

\paragraph{Sampling $z_t$} The conditional distribution of $z_t$ can be written as follows
\begin{eqnarray*}
p(z_t | \bm{K}, \bm{y}, \bm{z}_{\lnot t}, \bm{\theta}) & \propto & \int p(\bm{y} | \bm{f}, \bm{z}_{\lnot t}, z_t, \bm{\theta} ) p(\bm{f} | \bm{K}) d \bm{f}, \\
 & = & \int p(y_t | f_t, \theta_{z_t} ) p(f_t | \bm{y}, \bm{z}_{\lnot t}, \bm{\theta}, \bm{K}) df_t, \\
 & = & \textrm{WHAT THEN?}
\end{eqnarray*}

Explain why we can make the jump above.

The key bit is that $p(f_t | \bm{y}, \bm{z}_{\lnot t}, \bm{\theta}, \bm{K})$ is a Gaussian process where every datapoint contributes noise that is dependent on the CRP partition it belongs to.

\begin{equation}
\begin{pmatrix}
\bm{y} \\ f_t
\end{pmatrix}
\sim
\begin{pmatrix}
K(x_1,x_1) & K(x_1,x_2) & ... \\
K(x_1,x_1) & K(x_1,x_2) & ... \\
K(x_1,x_1) & K(x_1,x_2) & ... \\
\end{pmatrix}
\end{equation}

We know that [CITE Carl] $p(\bm{f} | \bm{K})$ can be represented as a multivariate Gaussian distribution.

%  & = & \int p(y_t | f_t, \theta_{z_t} ) p(f_t | \bm{f}, \bm{y}, \bm{z}_{\lnot t}, z_t, \bm{\theta}) p(\bm{y}_{\lnot t} | \bm{f)_{\lnot t},  \bm{z}_{\lnot t}, \bm{\theta}) p(\bm{f} | \bm{K}) d \bm{f}, \\

\paragraph{Sampling $\theta_n$}
